Stat 400 Project

### 2021-11-30 Stat 400 proj.Rmd
The coord_checker function works, it's just only bounded for positive points.

#Function for getting updated coordinates
update_coords <- function(og_df, delta_df){
  new_mx <- matrix(data=NA, nrow=nrow(og_df), ncol=2)
  new_df <- data.frame(new_mx)
  new_df[,1] <- as.numeric(og_df[,'x']) + delta_df[,'delta_x']
  new_df[,2] <- as.numeric(og_df[,'y']) + delta_df[,'delta_y']
  colnames(new_df) <- c('x', 'y')
  return(new_df)
}

@@

    if(i == 1){
    step_size <- get_step_length(initial_data, x_dim, y_dim)
    direction <- get_step_direction(step_size)
    change <- get_delts(step_size, direction)
    updated_positions <- update_coords(initial_data, change)
    updated_state <- cbind(updated_positions, initial_data[,3])
    new_status <- infection_status(updated_state, 2)
    end_day[[i]] <- cbind(updated_positions, new_status)
    }else{
    step_size <- get_step_length(initial_data, x_dim, y_dim)
    direction <- get_step_direction(step_size)
    change <- get_delts(step_size, direction)
    updated_positions <- update_coords(end_day[[i-1]], change)
    updated_state <- cbind(updated_positions, end_day[[i-1]]$new_status)
    new_status <- infection_status(updated_state, 1/5)
    end_day[[i]] <- cbind(updated_positions, new_status)

@@

#Testing
df <- starting_vals(100, 2, 10, 10)
len <- get_step_length(df, 10, 10)
dir <- get_step_direction(len)
delts <- get_delts(len, dir)
newdf <- update_coords(df, delts)

>>>>

#Function for getting updated coordinates
update_coords <- function(og_df, delta_df){
  new_mx <- matrix(data=NA, nrow=nrow(og_df), ncol=2)
  new_df <- data.frame(new_mx)
  new_df[,1] <- as.numeric(og_df[,'x']) + delta_df[,'delta_x']
  new_df[,2] <- as.numeric(og_df[,'y']) + delta_df[,'delta_y']
  colnames(new_df) <- c('x', 'y')
  new_df
}

coord_checker <- function(og_df, new_df, x_dim, y_dim){
  baddies <- NULL
  for(i in 1:nrow(new_df)){
    if(as.numeric(new_df[i, 'x']) > x_dim | as.numeric(new_df[i, 'y']) > y_dim){
      baddies <- append(baddies, i)
    }
  }

  if(is.null(baddies)){
    return(new_df)
  }else{
  new_step <- get_step_length(new_df[i,], x_dim, y_dim)
  new_direction <- get_step_direction(new_step)
  new_change <- get_delts(new_step, new_direction)
  new_df <- update_coords(og_df[baddies,], new_change)
  full_df <- rbind(new_df, og_df[-baddies, -3])
  return(coord_checker(og_df, full_df, x_dim, y_dim))
  }
}

@@

    if(i == 1){
    step_size <- get_step_length(initial_data, x_dim, y_dim)
    direction <- get_step_direction(step_size)
    change <- get_delts(step_size, direction)
    updated_positions <- update_coords(initial_data, change, x_dim, y_dim)
    # checked_positions <- coord_checker(og_df=initial_data, new_df=updated_positions, x_dim=x_dim, y_dim=y_dim)
    updated_state <- cbind(updated_positions, initial_data[,3])
    new_status <- infection_status(updated_state, 2)
    end_day[[i]] <- cbind(updated_positions, new_status)
    }else{
    step_size <- get_step_length(initial_data, x_dim, y_dim)
    direction <- get_step_direction(step_size)
    change <- get_delts(step_size, direction)
    updated_positions <- update_coords(end_day[[i-1]], change, x_dim, y_dim)
    updated_state <- cbind(updated_positions, end_day[[i-1]]$new_status)
    new_status <- infection_status(updated_state, 1/5)
    end_day[[i]] <- cbind(updated_positions, new_status)

@@

#Testing
df <- starting_vals(100, 2, 10, 10)
len <- get_step_length(df, 10, 10)
dir <- get_step_direction(len)
delts <- get_delts(len, dir)
newdf <- update_coords(df, delts)
coord_checker(df, newdf, 10, 10)

#S,I,R data
suceptable = function(){

}

recovered = function(){

}

infected = function(){

}
